---
title: East TN information
output: html_document
params:
  sumtab: "unknown"
---

The purpose of this is to gather information on how the covid-19 pandemic is progressing in East TN. There are good sites that have info on the pandemic generally across the US and world, but Tennessee as well as local entities put out info that is not captured by these sites. 

I am mostly doing this for my own curiosity as a parent in Oak Ridge, TN; though I work in science, I don't work in epidemiology. Thus, I'm not doing any calculations of future spread, etc. -- I'm taking published datasets and plotting them. For datasets that are presented as current conditions but do not have a history, I take a copy of them (usually every six hours) to be able to plot how they change over time.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("_packages.R")
source("R/functions.R")
tar_load(hospital_knox)
tar_load(daily_focal)
tar_load(tn_death_predictions)
tar_load(tn_death_history)
counties_in_hospital_region <- FocalCountiesEastTN()
last_hospital_update <- max(hospital_knox$Date)
daily_focal$PercentActive <- 100*daily_focal$TOTAL_ACTIVE/daily_focal$Population
daily_focal$PercentDead <- 100*daily_focal$TOTAL_DEATHS/daily_focal$Population
daily_focal$PercentHospitalized <- 100*daily_focal$TOTAL_HOSPITALIZED/daily_focal$Population
daily_focal$PercentConfirmed <- 100*daily_focal$TOTAL_CONFIRMED/daily_focal$Population
daily_region <- subset(daily_focal, Region=="East TN")
current_active_region <- daily_region$PercentActive[which.max(daily_region$DATE)]
current_percent_dead_region <- daily_region$PercentDead[which.max(daily_region$DATE)]
current_percent_hospitalized_region <- daily_region$PercentHospitalized[which.max(daily_region$DATE)]
current_percent_confirmed_region <- daily_region$PercentConfirmed[which.max(daily_region$DATE)]
neyland_capacity <- 102455
```

Currently, at least 1 of every `r round(100/current_active_region)` people in our region (`r round(current_active_region,2)`%) currently have covid infections (based on the tests reported to the state; additional people may have covid but have not been tested). Another way of looking at this: if UTK's Neyland Stadium had this percentage of people with active covid infections, `round(0.01*current_active_region*neyland_capacity)` people in the 102,455 person stadium would have covid right now (though hopefully people who know they are sick stay home). Over the course of the pandemic, `round(0.01*current_percent_dead_region*neyland_capacity)` people in a full stadium would have died from covid, `round(0.01*current_percent_hospitalized_region*neyland_capacity)` would have been hospitalized, and `round(0.01*current_percent_confirmed_region*neyland_capacity)` would have had a case of covid.

As of the last time the data were updated, the 19 regional hospitals around Knoxville had **only `r tail(subset(hospital_knox, Resource=="ICU Beds")$Available,1)` ICU beds available of `r tail(subset(hospital_knox, Resource=="ICU Beds")$Total.Capacity,1)` total**, based on info from the [Knox County Health Department](https://covid.knoxcountytn.gov/case-count.html).

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tn_death_predictions_point <- subset(tn_death_predictions, type=="point")

tn_death_prediction_organized <- data.frame(Date=tn_death_predictions_point$target_end_date,Expected_Deaths=tn_death_predictions_point$value, Range=rep(NA, nrow(tn_death_predictions_point)))
for (i in sequence(nrow(tn_death_prediction_organized))) {
	tn_death_prediction_organized$Range[i] <- paste0(subset(tn_death_predictions, quantile==0.025 & target_end_date== tn_death_prediction_organized$Date[i])$value, "-", subset(tn_death_predictions, quantile==0.975 & target_end_date== tn_death_prediction_organized$Date[i])$value)
}
tn_death_prediction_organized <- tn_death_prediction_organized[order(tn_death_prediction_organized$Date),]


#knitr::kable(tn_death_prediction_organized)
```

As of `r format(as.Date(tail(tn_death_history$target_end_date,1)),format="%a, %b %d, %Y")`, **`r format(tail(tn_death_history$value,1),big.mark=",",scientific=FALSE)` people have died from covid in Tennessee.** The [COVID-19 Forecast Hub](https://covid19forecasthub.org) makes predictions based on a number of models. They predict that **by `r format(as.Date(tn_death_prediction_organized$Date[1]),format="%b %d")`, an additional `r tn_death_prediction_organized$Expected_Deaths[1]` people (range `r tn_death_prediction_organized$Range[1]`) will have died from covid in Tennessee**, with `r tn_death_prediction_organized$Expected_Deaths[2]`, `r tn_death_prediction_organized$Expected_Deaths[3]`, and `r tn_death_prediction_organized$Expected_Deaths[4]` more covid deaths in each of the next three weeks.

See other pages from the menu above for more detail on vaccinations, conditions in schools, and more. *To get a vaccine to protect others and yourself, go to https://www.vaccines.gov/.*



```{r percentageactive, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Percentage of people in the region with active covid-19"}

active <- ggplot(daily_focal, aes(x=DATE, y=PercentActive, group=Region)) + geom_line(aes(colour=Region)) + ylab("Percent of people with active covid infections each day") + xlab("Date") + ylim(0,NA)  + scale_colour_viridis_d(end=0.8) + theme_light()

print(active)
```

A high level overview of the pandemic in Tennessee as a whole (using Tennessee's definitions of groups):

```{r, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
tar_load(sumtabfraction)
knitr::kable(sumtabfraction)
```
