---
title: East TN information
output:
  html_document:
    includes:
       in_header: GA_Script.html
params:
  sumtab: "unknown"
---

The purpose of this is to gather information on how the covid-19 pandemic is progressing in East TN. There are good sites that have info on the pandemic generally across the US and world, but Tennessee as well as local entities put out info that is not captured by these sites. 

I am mostly doing this for my own curiosity as a parent in Oak Ridge, TN; though I work in science, I don't work in epidemiology. Thus, I'm not doing any calculations of future spread, etc. -- I'm taking published datasets and plotting them. For datasets that are presented as current conditions but do not have a history, I take a copy of them (usually every six hours) to be able to plot how they change over time.

Use the menu above for information on vaccinations, conditions in schools, and more. This site was last updated on `r (format(Sys.time(), "%I:%M %p on %A %B %d, %Y"))`, though many data sources have a lag of a week or more. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("_packages.R")
source("R/functions.R")
tar_load(hospital_knox)
tar_load(daily_focal)
tar_load(tn_death_predictions)
tar_load(tn_death_history)

tar_load(cdc_all_reports)
cdc_knox <- GetCommunityLevel(subset(cdc_all_reports, FIPS==047093))
cdc_knox$County <- "Knox"
cdc_anderson <- GetCommunityLevel(subset(cdc_all_reports, FIPS==047001))
cdc_anderson$County <- "Anderson"
cdc_local <- rbind(cdc_knox, cdc_anderson) 
cdc_local <- subset(cdc_local, Cases_7_days_per_100K_County>0) # since these reflect lack of reporting
cdc_local$Date <- as.Date(cdc_local$ReportDate, format="%Y%m%d")

tar_load(cdc_transmission_new_2022)
cdc_knox_transmission <- subset(cdc_transmission_new_2022, fips_code==047093)
cdc_knox_transmission$County <- "Knox"
cdc_anderson_transmission <- subset(cdc_transmission_new_2022, fips_code==047001)
cdc_anderson_transmission$County <- "Anderson"
cdc_local_transmission <- rbind(cdc_knox_transmission, cdc_anderson_transmission) 
cdc_local_transmission$Date <- as.Date(cdc_local_transmission$report_date, format="%Y/%m/%d")
cdc_local_transmission <- cdc_local_transmission[!is.na(cdc_local_transmission$percent_test_results_reported_positive_last_7_days),]




counties_in_hospital_region <- FocalCountiesEastTN()
last_hospital_update <- max(hospital_knox$Date)
#daily_focal$PercentActive <- 100*daily_focal$TOTAL_ACTIVE/daily_focal$Population
daily_focal$PercentDead <- 100*daily_focal$TOTAL_DEATHS/daily_focal$Population
daily_focal$PercentHospitalized <- 100*daily_focal$TOTAL_HOSPITALIZED/daily_focal$Population
daily_focal$PercentConfirmed <- 100*daily_focal$TOTAL_CONFIRMED/daily_focal$Population
daily_region <- subset(daily_focal, Region=="East TN")
#current_active_region <- daily_region$PercentActive[which.max(daily_region$DATE)]
current_percent_dead_region <- daily_region$PercentDead[which.max(daily_region$DATE)]
current_percent_hospitalized_region <- daily_region$PercentHospitalized[which.max(daily_region$DATE)]
current_percent_confirmed_region <- daily_region$PercentConfirmed[which.max(daily_region$DATE)]
neyland_capacity <- 102455
```

As of the last time the data were updated, the 19 regional hospitals around Knoxville had **only `r tail(subset(hospital_knox, Resource=="ICU Beds")$Available,1)` ICU beds available of `r tail(subset(hospital_knox, Resource=="ICU Beds")$Total.Capacity,1)` total**, based on info from the [Knox County Health Department](https://covid.knoxcountytn.gov/case-count.html).

```{r, echo=FALSE, message=FALSE, warning=FALSE}

	tn_death_predictions_point <- subset(tn_death_predictions, type=="point")

	tn_death_prediction_organized <- data.frame(Date=tn_death_predictions_point$target_end_date,Expected_Deaths=tn_death_predictions_point$value, Range=rep(NA, nrow(tn_death_predictions_point)))
	for (i in sequence(nrow(tn_death_prediction_organized))) {
		tn_death_prediction_organized$Range[i] <- paste0(subset(tn_death_predictions, quantile==0.025 & target_end_date== tn_death_prediction_organized$Date[i])$value, "-", subset(tn_death_predictions, quantile==0.975 & target_end_date== tn_death_prediction_organized$Date[i])$value)
	}
	tn_death_prediction_organized <- tn_death_prediction_organized[order(tn_death_prediction_organized$Date),]


#knitr::kable(tn_death_prediction_organized)
```

As of `r format(as.Date(tail(tn_death_history$target_end_date,1)),format="%a, %b %d, %Y")`, **`r format(tail(tn_death_history$value,1),big.mark=",",scientific=FALSE)` people have died from covid in Tennessee.** 

The [COVID-19 Forecast Hub](https://covid19forecasthub.org) makes predictions based on a number of models every week. They predict that in the week ending on **`r format(as.Date(tn_death_prediction_organized$Date[1]),format="%b %d")`, an additional `r tn_death_prediction_organized$Expected_Deaths[1]` people (range `r tn_death_prediction_organized$Range[1]`) will have died from covid in Tennessee**, with `r tn_death_prediction_organized$Expected_Deaths[2]` more covid deaths by `r format(as.Date(tn_death_prediction_organized$Date[2]),format="%b %d")`.

*To get a vaccine to protect others and yourself, go to https://www.vaccines.gov/.*

CDC provides [two different ways](https://www.cdc.gov/coronavirus/2019-ncov/science/science-briefs/indicators-monitoring-community-levels.html) of summarizing covid in a community:

* **Community Transmission** refers to measures of the presence and spread of SARS-CoV-2, the virus that causes COVID-19. This is used in the blue / yellow / orange / red maps, like [here](https://covid.cdc.gov/covid-data-tracker/#county-view?list_select_state=all_states&list_select_county=all_counties&data-type=Risk&null=Risk).
* **COVID-19 Community Levels** refer to the measures of the impact of COVID-19 in terms of hospitalizations and healthcare system strain, while accounting for transmission in the community. This is used in the pastel yellow / green / orange map (red does not exist), like [here](https://covid.cdc.gov/covid-data-tracker/#county-view?list_select_state=all_states&list_select_county=all_counties&data-type=CommunityLevels&null=CommunityLevels).

The plot below uses color to indicate community transmission -- how the disease is spreading. For the y-axis, I am showing the test positivity rate, though this is less informative as testing and reporting of tests drop off.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Positivity rate and CDC transmission level"}
cdc_local_transmission$`Community Transmission Level` <- factor(stringr::str_to_title(cdc_local_transmission$community_transmission_level), levels = c("Low", "Moderate", "Substantial", "High"))

cdc_transmission_plot <- ggplot(cdc_local_transmission, aes(x=Date, y=percent_test_results_reported_positive_last_7_days, color=`Community Transmission Level`)) + scale_color_manual(values=c("dodgerblue", "yellow2", "darkorange", "red1")) + geom_point() + ylab("Positivity rate over last 7 days") + xlab("Date") + facet_wrap(~ County, ncol=1) 
print(cdc_transmission_plot)
```


We can plot using the [Feb 2022 guidelines from the CDC](https://www.cdc.gov/coronavirus/2019-ncov/your-health/covid-by-county.html) for low, medium, high community level; I've also recalculated past data so we can see how it would apply then. Note that though I plot case numbers, which are used by the CDC among other metrics, these might not be the most informative given the current state of testing; the hospitalization data (see tab above) could be useful.


```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Cases per 100K and CDC color"}
cdc_local$`Community Level` <- factor(cdc_local$New_Community_Level, levels = c("Low", "Medium", "High"))

cdc_new_plot <- ggplot(cdc_local, aes(x=Date, y=Cases_7_days_per_100K_County, color=`Community Level`)) + scale_color_manual(values=c("mediumseagreen", "gold2", "orangered2")) + geom_point() + ylab("Seven day number of covid cases per 100K people") + xlab("Date") + facet_wrap(~ County, ncol=1) 
print(cdc_new_plot)
```


Here are the percent of tests positive, averaged over a week.

```{r percentagpositive, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Percentage of positive tests over time"}

positivity <- ggplot(daily_focal, aes(x=DATE, y=PositivityPercentage_per_week, group=Region)) + geom_line(aes(colour=Region)) + ylab("Percent of positive tests reported to state") + xlab("Date") + ylim(0,NA)  + scale_colour_viridis_d(end=0.8) + theme_light() + theme(legend.justification = c(0, 1), legend.position = c(0.1, .9))

print(positivity)
```



Here are the deaths over time associated with covid in East TN (excluding Dec 22, 2021, when there seems to be an error in the state's death records).  

```{r deaths, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Covid associated deaths over time"}
daily_focal_easttn <- subset(daily_focal, Region=="East TN")
daily_focal_easttn <- subset(daily_focal_easttn, DATE!=as.Date("20211222", format="%Y%m%d"))
try(daily_death_plot <- ggplot(daily_focal_easttn, aes(x=DATE, y=NEW_DEATHS)) + theme_light() + geom_ma(aes( linetype="a"), n=7) +  guides(linetype = "none") + ylab("Deaths per day (7 day average)") + xlab("Date") + ggtitle("Covid-Associated Deaths in East TN") )
try(print(daily_death_plot))

```



```{r percentageactive, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, fig.alt="Percentage of people in the region with active covid-19"}
# Here are the percent of people who have active covid cases right now, who have tested and gotten positive tests, *and* who have reported this to the state. 
 
active <- ggplot(daily_focal, aes(x=DATE, y=PercentActive, group=Region)) + geom_line(aes(colour=Region)) + ylab("Percent of people with active covid infections each day") + xlab("Date") + ylim(0,NA)  + scale_colour_viridis_d(end=0.8) + theme_light() + theme(legend.justification = c(0, 1), legend.position = c(0.1, .9)) 

print(active)
```



A high level overview of the pandemic in Tennessee as a whole (using Tennessee's definitions of groups):

```{r, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
tar_load(sumtabfraction)
knitr::kable(sumtabfraction)
```
