---
title: Individual Hospitals
output:
  html_document:
    includes:
       in_header: GA_Script.html
---

## No more data

July 27, 2023: The data sources I was using for this site are no longer being updated. The only remaining sources seem to be sewage data; CDC has it [https://covid.cdc.gov/covid-data-tracker/#wastewater-surveillance](here) but it's all relative (Covid levels in sewage versus the highest at any point at that site, but sites came online at different times). Biobot Analytics has data on absolute numbers through time (as well as variants) [https://biobot.io/data/covid-19](here) but they no longer have freely accessible raw data. Even hospitals release data only sporadically and incompletely now. I might poke around later to see what's available but for now I'm not updating this site.

### Old site

The US Department of Health and Human Services gives data on hospital usage. Here are data for hospitals in our area. Note that many have apparently stopped reporting their information.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("_packages.R")
source("R/functions.R")
tar_load(hhs_capacity_tn)
tar_load(hhs_capacity_tn_focal)
tar_load(hhs_capacity_tn_focal_latest_pretty)
knitr::kable(hhs_capacity_tn_focal_latest_pretty)
```

Plotting percentage of ICU patients with covid over time. Some hospitals have much more frequently updated data than others.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=30}
try(hospital_plot <- ggplot(hhs_capacity_tn_focal, aes(x=DATE, y=percentage_adult_hospital_inpatient_ICU_bed_occupied_of_all_inpatient_ICU_beds)) + geom_point(aes(colour=hospital_name)) + theme_light() + ylab("Percent of ICU patients witth covid") + xlab("Date") + ggtitle("Percent of ICU patients with covid") + facet_wrap(~ hospital_name, ncol=2) + ylim(c(60, 100)) +   guides(colour=FALSE) )
print(hospital_plot)
```

```{r, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.height=30}
try(hospital_plot_beds <- ggplot(hhs_capacity_tn_focal, aes(x=DATE, y=number_unoccupied_adult_hospital_ICU_beds)) + geom_line(aes(colour=hospital_name)) + theme_light() + ylab("Number of available ICU beds") + xlab("Date") + ggtitle("Number of available ICU beds") + facet_wrap(~ hospital_name, ncol=2) + ylim(c(60, 100)) +  guides(colour=FALSE) )
print(hospital_plot_beds)
```
