---
title: Knox County Schools
output:
  html_document:
    includes:
       in_header: GA_Script.html
---

Knox County Schools are releasing information at https://www.knoxschools.org/covid, I take a snapshot of this every 24 hours and plot it.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Line plot of active covid cases"}

source("_packages.R")
tar_load(schools_knox)
schools_knox <- schools_knox[!is.na(schools_knox$Active_Students_Count),]

tar_load(schoolkids_daily)
schools_knox_counts <- data.frame(Date=rep(schools_knox$Date,2), Count=c(schools_knox$Active_Students_Count, schools_knox$Active_Staff_Count), Population=c(rep("Student", nrow(schools_knox)), rep("Staff", nrow(schools_knox))))

try(knox_schools_ytd <- ggplot(schools_knox_counts, aes(x=Date, y=Count, group=Population)) + geom_line(aes(colour=Population)) + theme_light() + ylab("Number of individuals with active covid infections") + xlab("Date") + ggtitle("Counts of covid infections in Knox County Schools, TN"))
print(knox_schools_ytd)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Line plot of active covid cases now in Oak Ridge schools"}


schools_knox_percent <- data.frame(Date=rep(schools_knox$Date,2), Percent=c(schools_knox$Active_Students_Percent, schools_knox$Active_Staff_Percent), Population=c(rep("Student", nrow(schools_knox)), rep("Staff", nrow(schools_knox))))



try(knox_schools_pct <- ggplot(schools_knox_percent, aes(x=Date, y=Percent, group=Population)) + geom_line(aes(colour=Population)) + theme_light() + ylab("Percent of individuals with active covid infections") + xlab("Date") + ggtitle("Percentage of covid infections in Knox County Schools, TN"))
print(knox_schools_pct)
```

We can also compare Knox County Schools to what the state has for students age 5-17 who live in Knox County (who include the students enrolled in the public schools, but also those who go to private schools, who go out of the district, etc.). The state data includes new cases, while Knox County Schools only includes active cases, which depending on definition can be all of those who have been 10 days or 14 days since the onset of symptoms and who have a positive test result.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="school vs state data"}
schoolkids_knox <- subset(schoolkids_daily, Region=="Knox County")
active_knox <- data.frame(DATE=rep(schoolkids_knox$DATE,2), ACTIVE_CASES=c(zoo::rollsum(schoolkids_knox$NEW_CASES, k=10, align="right", fill=NA), zoo::rollsum(schoolkids_knox$NEW_CASES, k=14, align="right", fill=NA)), POPULATION=c(rep("Knox County ('Active' = 10 days, age 5-17)", nrow(schoolkids_knox)), rep("Knox County ('Active' = 14 days, age 5-17)", nrow(schoolkids_knox)))) 
active_knox <- rbind(active_knox, data.frame(DATE=schools_knox$Date, ACTIVE_CASES=schools_knox$Active_Students_Count, POPULATION=rep("Knox Schools Only Data", nrow(schools_knox))))


try(knox_schools_vs_state <- ggplot(subset(active_knox, DATE>=as.Date("2021-06-01")), aes(x=DATE, y=ACTIVE_CASES, group=POPULATION)) + geom_line(aes(colour=POPULATION)) + theme_light() + ylab("Number of active covid cases for\npeople of student age in Knox County") + xlab("Date") + ggtitle("Percentage of covid infections in Knox County Schools, TN"))
print(knox_schools_vs_state)
```

I also maintain [vaccication.org](http://vaccication.org). This has information about vaccination in various US counties; below is the page for Knox County. Pay special note to the vaccination rate for those age 12-18.

<iframe src='https://vaccication.org/counties/Knox_TN.html' width="100%" height=1600></iframe>