---
title: Knox County Schools
output:
  html_document:
    includes:
       in_header: GA_Script.html
---

### 2022-2023

No data are being released.

### 2021-2022

This is from daily data scraped from Knox County Schools' website. See also this page populated by parents and guardians of students as an unofficial project, which gives more granular data on individual schools: https://kcsdashboard.org/.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Line plot of active covid cases"}

source("_packages.R")
tar_load(schools_knox)
tar_load(individual_schools_knox)
tar_load(kcs_dashboard)
individual_schools_most_recent <- subset(individual_schools_knox, Date == max(Date))
schools_knox <- schools_knox[!is.na(schools_knox$Active_Students_Count),]

tar_load(schoolkids_daily)
schools_knox_counts <- data.frame(Date=rep(schools_knox$Date,2), Count=c(schools_knox$Active_Students_Count, schools_knox$Active_Staff_Count), Population=c(rep("Student", nrow(schools_knox)), rep("Staff", nrow(schools_knox))))

try(knox_schools_ytd <- ggplot(schools_knox_counts, aes(x=Date, y=Count, group=Population)) + geom_line(aes(colour=Population)) + theme_light() + ylab("Number of individuals with active covid infections") + xlab("Date") + ggtitle("Counts of covid infections in Knox County Schools, TN"))
print(knox_schools_ytd)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Line plot of active covid cases now in Knox County schools"}


schools_knox_percent <- data.frame(Date=rep(schools_knox$Date,2), Percent=c(schools_knox$Active_Students_Percent, schools_knox$Active_Staff_Percent), Population=c(rep("Student", nrow(schools_knox)), rep("Staff", nrow(schools_knox))))



try(knox_schools_pct <- ggplot(schools_knox_percent, aes(x=Date, y=Percent, group=Population)) + geom_line(aes(colour=Population)) + theme_light() + ylab("Percent of individuals with active covid infections") + xlab("Date") + ggtitle("Percentage of covid infections in Knox County Schools, TN"))
print(knox_schools_pct)
```


### Individual Schools {#byschool}


Knox County Schools now have data on individual schools. We can see the percentage of students and staff in each school (those absent could be out for many different reasons, not just covid). Schools are aggregated by type: elementary, middle, high school, or other (such as Knox Adaptive Education Center or Richard Yoakley Alternative School). Note that lines do not change over school breaks.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="percentage of staff and students present"}
#present_plot <- ggplot(individual_schools_most_recent, aes(x=Student_Present_Percent, y=Staff_Present_Percent, group=Level, text=School)) + geom_point(aes(colour=Level)) + theme_light() + ylab("Percentage of staff present") + xlab("Percentage of students present") + ylim(c(60, 100)) + xlim(c(60, 100)) + ggtitle(paste0("Attendance in each school as of ", as.Date(max(individual_schools_most_recent$Date),"%b %d, %Y")))
#print(present_plot)


individual_schools_knox$Student_Enrolled <- as.numeric(individual_schools_knox$Student_Enrolled)
individual_schools_knox$Student_Present <- as.numeric(individual_schools_knox$Student_Present)
individual_schools_knox$Staff_Employed <- as.numeric(individual_schools_knox$Staff_Employed)
individual_schools_knox$Staff_Present <- as.numeric(individual_schools_knox$Staff_Present)
individual_schools_knox <- individual_schools_knox[!is.na(individual_schools_knox$Student_Enrolled),]

#all_schools_knox <- individual_schools_knox %>% group_by(Date, Level) %>% summarise(Student_Enrolled=sum(Student_Enrolled), Student_Present=sum(Student_Present), Staff_Employed=sum(Staff_Employed), Staff_Present=sum(Staff_Present))
#all_schools_knox$Student_Present_Percent <- 100*all_schools_knox$Student_Present/#all_schools_knox$Student_Enrolled
#all_schools_knox$Staff_Present_Percent <- 100*all_schools_knox$Staff_Present/#all_schools_knox$Staff_Employed

#all_schools_knox_vertical <- rbind(
#	data.frame(Date=all_schools_knox$Date, Level=all_schools_knox$Level, Percent_Present=all_schools_knox$Student_Present_Percent, Population="Student"),
#	data.frame(Date=all_schools_knox$Date, Level=all_schools_knox$Level, Percent_Present=all_schools_knox$Staff_Present_Percent, Population="Staff")
#)

#try(knox_schools_aggregate <- ggplot(all_schools_knox_vertical, aes(x=Date, y=Percent_Present, group=Population)) + geom_line(aes(colour=Population)) + theme_light() + ylab("Percentage in attendance") + xlab("Date") + ylim(c(60, 100)) + ggtitle("Attendance in Knox County Schools") + facet_wrap(~ Level, ncol=2) + scale_x_datetime(date_labels = "%b %d"))
#print(knox_schools_aggregate)
```

Plotting this by individual school over time, students first:

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=30, fig.alt="percentage of students present by school"}

individual_schools_knox$School <- gsub(" School", "", individual_schools_knox$School)
individual_schools_knox$School <- gsub(" Academy", "", individual_schools_knox$School)


try(knox_schools_ytd <- ggplot(individual_schools_knox, aes(x=Date, y=Student_Present_Percent, group=School)) + geom_point(aes(colour=Student_Present_Percent)) + theme_light() + ylab("Percentage of students in attendance") + xlab("Date") + ylim(c(60, 100)) + ggtitle("Student attendance in Knox County Schools") + facet_wrap(~ School, ncol=3) + theme(legend.position = "none") + scale_x_datetime(date_labels = "%b %d") + scale_colour_gradient2(mid="purple", midpoint=85, high="blue", low="red"))
print(knox_schools_ytd)
```

And staff:

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=30, fig.alt="percentage of staff present by school"}

try(knox_schools_staff_ytd <- ggplot(individual_schools_knox, aes(x=Date, y=Staff_Present_Percent, group=School)) + geom_point(aes(colour=Staff_Present_Percent)) + theme_light() + ylab("Percentage of staff in attendance") + xlab("Date") + ylim(c(60, 100)) + ggtitle("Staff attendance in Knox County Schools") + facet_wrap(~ School, ncol=3) + theme(legend.position = "none") + scale_x_datetime(date_labels = "%b %d") + scale_colour_gradient2(mid="purple", midpoint=85, high="blue", low="red"))
print(knox_schools_staff_ytd)
```


### Family-Provided Data {#diy}

Using data kindly provided by the [KCS DIY COVID-19 Dashboard](https://kcsdashboard.org/) from reports by families directly, we can see how long students have gone from having symptoms to getting a positive test result:

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="first symptoms vs first test"}
kcs_dashboard$ElapsedDays <- as.numeric(as.Date(kcs_dashboard$Positive.Test.Date) - as.Date(kcs_dashboard$Symptomatic.Date))
kcs_dashboard$Grade <- factor(kcs_dashboard$Grade,levels = c("K", sequence(12)))

days_plot <- ggplot(kcs_dashboard, aes(ElapsedDays)) + geom_bar() + theme_light() + ylab("Number of cases") + xlab("Days from first symptoms to first positive test") + ggtitle("Days from first symptoms to first positive test in Knox County Schools")
print(days_plot)
```

We can also see which grades have the most student reports from this family-provided data. However, this only comes from `r nrow(kcs_dashboard)` student cases, while far more than `r max(schools_knox$Active_Students_Count, na.rm=TRUE)` students have gotten covid in 2021-2022 school year in Knox County Schools (this is a major underestimate: the school system only releases the number of active cases, not new cases, so the number above is the most in any one day with covid). The DIY dashboard dataset has much more detail -- Knox County Schools is giving no indication of cases by grade, for example. To report your student's own case to the DIY dashboard, go to [https://kcsdashboard.org/reports/create](https://kcsdashboard.org/reports/create) and fill out the form.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="distribution by grade"}
grade_plot <- ggplot(kcs_dashboard, aes(Grade)) + geom_bar() + theme_light() + ylab("Number of cases") + xlab("Grade") + ggtitle("KCS cases by grade, as reported at KCS DIY dashboard")
print(grade_plot)
```

### County-Provided vs State-Provided Data {#countyvsstate}

We can also compare Knox County Schools to what the state has for students age 5-17 who live in Knox County (who include the students enrolled in the public schools, but also those who go to private schools, who go out of the district, etc.). The state data includes new cases, while Knox County Schools only includes active cases, which depending on definition can be all of those who have been 10 days or 14 days since the onset of symptoms and who have a positive test result. 

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="school vs state data"}
schoolkids_knox <- subset(schoolkids_daily, Region=="Knox County")
active_knox <- data.frame(DATE=rep(schoolkids_knox$DATE,2), ACTIVE_CASES=c(zoo::rollsum(schoolkids_knox$NEW_CASES, k=10, align="right", fill=NA), zoo::rollsum(schoolkids_knox$NEW_CASES, k=14, align="right", fill=NA)), POPULATION=c(rep("Knox County ('Active' = 10 days, age 5-17)", nrow(schoolkids_knox)), rep("Knox County ('Active' = 14 days, age 5-17)", nrow(schoolkids_knox)))) 
active_knox <- rbind(active_knox, data.frame(DATE=schools_knox$Date, ACTIVE_CASES=schools_knox$Active_Students_Count, POPULATION=rep("Knox Schools Only Data", nrow(schools_knox))))


try(knox_schools_vs_state <- ggplot(subset(active_knox, DATE>=as.Date("2021-06-01")), aes(x=DATE, y=ACTIVE_CASES, group=POPULATION)) + geom_line(aes(colour=POPULATION)) + theme_light() + ylab("Number of active covid cases for\npeople of student age in Knox County") + xlab("Date") + ggtitle("Percentage of covid infections in Knox County Schools, TN"))
print(knox_schools_vs_state)
```
