---
title: Last Four Weeks
output:
  html_document:
    includes:
       in_header: GA_Script.html
---


```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("_packages.R")
source("R/functions.R")
tar_load(hospital_knox)
tar_load(daily_focal)
counties_in_hospital_region <- FocalCountiesEastTN()
last_hospital_update <- max(hospital_knox$Date)
elapsed_seconds <- 28*24*60*60 # for 28 days
daily_focal$PercentActive <- 100*daily_focal$TOTAL_ACTIVE/daily_focal$Population
daily_focal$PercentDead <- 100*daily_focal$TOTAL_DEATHS/daily_focal$Population
daily_focal$PercentHospitalized <- 100*daily_focal$TOTAL_HOSPITALIZED/daily_focal$Population
daily_focal$PercentConfirmed <- 100*daily_focal$TOTAL_CONFIRMED/daily_focal$Population
daily_region <- subset(daily_focal, Region=="East TN")



tar_load(schools_knox)
tar_load(individual_schools_knox)
tar_load(kcs_dashboard)
schools_knox <- schools_knox[!is.na(schools_knox$Active_Students_Count),]

schools_knox_percent_for_focal <- data.frame(DATE=rep(schools_knox$Date,2), PercentActive=c(schools_knox$Active_Students_Percent, schools_knox$Active_Staff_Percent), Region=c(rep("KCS student", nrow(schools_knox)), rep("KCS staff", nrow(schools_knox))))

tar_load(schools_oakridge)
schools_oakridge_total <- subset(schools_oakridge, School=='Totals for the District')
schools_oakridge_for_focal <- data.frame(DATE=schools_oakridge_total$Date, PercentActive=schools_oakridge_total$PercentActiveCovidStudents, Region="ORS student")

```

We can focus on just the last four weeks, as some past peaks may obscure local dynamics otherwise.

Total people in the area who have active covid infections right now *and* for whom this has been reported to the state. There is all East TN as well as Knox and Anderson counties.

```{r percentageactive, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Percentage of people in the region with active covid-19"}


active <- ggplot(subset(daily_focal, daily_focal$DATE >= daily_focal$DATE[nrow(daily_focal)]-elapsed_seconds), aes(x=DATE, y=PercentActive, group=Region)) + geom_line(aes(colour=Region)) + ylab("Percent of people with active covid infections each day") + xlab("Date") + ylim(0,NA)  + scale_colour_viridis_d(end=0.8) + theme_light()

print(active)
```

We can also look at people in Knox County Schools (KCS) and Oak Ridge Schools (ORS)

```{r percentageactiveschools, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Percentage of people in the region with active covid-19"}

schools <- rbind(schools_knox_percent_for_focal, schools_oakridge_for_focal)


active <- ggplot(subset(schools, schools$DATE >= schools$DATE[nrow(schools)]-elapsed_seconds), aes(x=DATE, y=PercentActive, group=Region)) + geom_line(aes(colour=Region)) + ylab("Percent of people with active covid infections each day") + xlab("Date") + ylim(0,NA) + scale_colour_viridis_d(end=0.8) + theme_light()

print(active)
```

We can also look at deaths per day, though this lags infections by weeks:

```{r numberdead, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Covid deaths per day"}

deaths <- ggplot(subset(daily_focal, daily_focal$DATE >= daily_focal$DATE[nrow(daily_focal)]-elapsed_seconds), aes(x=DATE, y=NEW_DEATHS, group=Region)) + geom_ma(aes(colour=Region, linetype="a"), n=7) + guides(linetype = "none") + ylab("Number of covid deaths per day (7 day average)") + xlab("Date") + ylim(0,NA)  + scale_colour_viridis_d(end=0.8) + theme_light()

print(deaths)
```

The [Knox County Health Department](https://covid.knoxcountytn.gov) puts out information on hospital capacity in their region, which is `r paste0(sort(counties_in_hospital_region), collapse=", ")` Counties; there are 19 hospitals in this region with potential ICU beds.


```{r hospitalcapacityplot, echo=FALSE, message=FALSE, warning=FALSE}
try(hosp_plot <- ggplot(subset(hospital_knox, Date>=max(hospital_knox$Date)-elapsed_seconds), aes(x=Date, y=Current.Utilization, group=Resource)) + geom_line(aes(colour=Resource)) +  ylab("Percent Utilization in East Tennessee Region") + xlab("Date") + ylim(0,100) + theme_light() + scale_colour_viridis_d(end=0.8) + geom_hline(yintercept=100, col="red"))
try(print(hosp_plot))

```

