---
title: Risk by Activity
output:
  html_document:
    includes:
       in_header: GA_Script.html
---


The [microCOVID Project](https://microcovid.org/) is a service that uses the best available data to estimate the risk of different activities. It does not replace advice from a medical professional, but as a way to deciding how to balance risk, it can be useful. It computes "microcovids," a one in a million chance of getting covid: every 10,000 microcovids means a 1% chance of getting covid at the event. I created a set of scenarios that may represent potential events in East Tennessee; for each one, the expected probability of getting covid at that event per event, based on microcovid's data, is shown. For each, the risk is shown for someone vaccinated and masked, vaccinated but not masked, and not vaccinated nor masked. You can go to the linked page for each to change the parameters. These numbers are as of Nov. 23, 2021.

Microcovid.org's point estimate the percentage chance of getting covid in a one hour lecture for someone (the rows) with a classroom of people with vaccination state matching that of Knox County and with different masks as columns. Note that these are their risk of getting it; it does not capture how severe the disease is (vaccination dramatically cuts the risk of death if you do get covid, for example):

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Per class risk"}
tar_load(microcovid_summary)
knitr::kable(microcovid_summary[[1]])
```

And the same percentage chance of getting covid over six class sessions with these conditions;


```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Per class risk"}
tar_load(microcovid_summary)
knitr::kable(microcovid_summary[[2]])
```

