---
title: Risk by Activity
output:
  html_document:
    includes:
       in_header: GA_Script.html
---


The [microCOVID Project](https://microcovid.org/) is a service that uses the best available data to estimate the risk of different activities. It does not replace advice from a medical professional, but as a way to deciding how to balance risk, it can be useful. It computes "microcovids," a one in a million chance of getting covid: every 10,000 microcovids means a 1% chance of getting covid at the event.

Microcovid.org's point estimate the percentage chance of getting covid in a one hour lecture for someone (the rows) with a classroom of people with vaccination state matching that of Knox County and with different masks as columns. You can see the details of the scenario I set up [here](https://www.microcovid.org/?distance=normal&duration=60&interaction=oneTime&personCount=10&riskProfile=average&scenarioName=custom&setting=indoor&subLocation=US_47093&theirMask=none&topLocation=US_47&voice=normal&yourMask=basic&yourVaccineDoses=2&yourVaccineType=pfizer); you can change your vaccination and masks, the classroom's conditions, etc. Note that the numbers is the probability of the focal person getting covid; it does not capture how severe the disease is (vaccination dramatically cuts the risk of death if you do get covid, for example):

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Per class risk"}
tar_load(microcovid_summary)
knitr::kable(microcovid_summary[[1]])
```

And the same percentage chance of getting covid over six class sessions with these conditions;


```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Per class risk"}
tar_load(microcovid_summary)
knitr::kable(microcovid_summary[[2]])
```

