---
title: Risk by Activity
output:
  html_document:
    includes:
       in_header: GA_Script.html
---

## No more data

July 27, 2023: The data sources I was using for this site are no longer being updated. The only remaining sources seem to be sewage data; CDC has it [https://covid.cdc.gov/covid-data-tracker/#wastewater-surveillance](here) but it's all relative (Covid levels in sewage versus the highest at any point at that site, but sites came online at different times). Biobot Analytics has data on absolute numbers through time (as well as variants) [https://biobot.io/data/covid-19](here) but they no longer have freely accessible raw data. Even hospitals release data only sporadically and incompletely now. I might poke around later to see what's available but for now I'm not updating this site.

### Old site


The [microCOVID Project](https://microcovid.org/) is a service that uses the best available data to estimate the risk of different activities. It does not replace advice from a medical professional, but as a way to deciding how to balance risk, it can be useful. It computes "microcovids," a one in a million chance of getting covid: every 10,000 microcovids means a 1% chance of getting covid at the event.

Microcovid.org's point estimate the percentage chance of getting covid in a one hour lecture for someone (the rows) with a classroom of people with vaccination state matching that of Knox County and with different masks as columns. You can see the details of the scenario I set up [here](https://www.microcovid.org/?distance=normal&duration=60&interaction=oneTime&personCount=10&riskProfile=average&scenarioName=custom&setting=indoor&subLocation=US_47093&theirMask=none&topLocation=US_47&voice=normal&yourMask=basic&yourVaccineDoses=2&yourVaccineType=pfizer); you can change your vaccination and masks, the classroom's conditions, etc. Note that the numbers are the odds of the focal person getting covid; it does not capture how severe the disease is (vaccination dramatically cuts the risk of death if you do get covid, for example):

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Per class risk"}
tar_load(microcovid_summary)
#microcovid_summary[[1]] <- paste0(microcovid_summary[[1]], '%')
knitr::kable(microcovid_summary[[1]])
```

And the same probability of getting covid over *six* class sessions with these conditions;


```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Per class risk"}
tar_load(microcovid_summary)
#microcovid_summary[[2]] <- paste0(microcovid_summary[[2]], '%')
knitr::kable(microcovid_summary[[2]])
```

