---
title: Oak Ridge Schools
output:
  html_document:
    includes:
       in_header: GA_Script.html
---

### 2022-2023

For the 2022-2023 school year, Oak Ridge Schools are not reporting details of covid incidence or requiring any mitigation measures. 

### 2021-2022 

Oak Ridge Schools were releasing information on cases in schools from August 2021 to mid-March 2022. You can also get information at https://www.oakridger.com/ and https://oakridgetoday.com/. 

The plot below shows the proportion of students with active covid cases at any one time over the 2021-2022 school year. 

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Line plot of active covid cases now in Oak Ridge schools"}
source("_packages.R")
tar_load(schools_oakridge)
nonzero_schools <- unique(subset(schools_oakridge, PercentPositiveStudentsYearToDate>0)$School)
nonzero_schools <- nonzero_schools[!grepl("Totals for",nonzero_schools)]
schools_oakridge_nonzero <- schools_oakridge[which(schools_oakridge$School %in% nonzero_schools),]
data_ends <- subset(schools_oakridge_nonzero, Date==max(schools_oakridge$Date))
data_ends$Label <- paste0(data_ends$School, " (", round(data_ends$PercentActiveCovidStudents,1), '%)')
schools_oakridge_nonzero$PercentActiveCovidStudents <- as.numeric(schools_oakridge_nonzero$PercentActiveCovidStudents)
#try(oakridge_schools_active <- ggplot(schools_oakridge_nonzero, aes(x=Date, y=PercentActiveCovidStudents, group=School)) + geom_point(aes(colour=School)) + theme_light() + ylab("Percentage of students with active covid infections") + xlab("Date") + ggtitle("Student active covid infections in Oak Ridge, TN") + scale_color_discrete(guide = FALSE) + scale_y_continuous(sec.axis = sec_axis(~ ., labels=data_ends$Label, breaks = data_ends$PercentActiveCovidStudents)) + facet_wrap(~ School, ncol=3))
try(oakridge_schools_active <- ggplot(schools_oakridge_nonzero, aes(x=Date, y=PercentActiveCovidStudents, group=School)) + geom_point(aes(colour=PercentActiveCovidStudents)) + scale_colour_gradient2(mid="purple", midpoint=1.5, high="red", low="blue") + theme_light() + ylab("Percentage of students with active covid infections") + xlab("Date") + ggtitle("Student active covid infections in Oak Ridge, TN") + facet_wrap(~ School, ncol=3) + theme(legend.position = "none") )

print(oakridge_schools_active)
```

What percentage of students in a school have gotten covid over the 2021-2022 year alone? Note that this assumes each student gets covid no more than once. However, a bout of covid gives only partial immunity, so some students may have had covid more than once.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Line plot of positive covid cases year to date"}
data_ends <- subset(schools_oakridge_nonzero, Date==max(schools_oakridge$Date))
data_ends$Label <- paste0(data_ends$School, " (", round(data_ends$PercentPositiveStudentsYearToDate,1), '%)')
#try(oakridge_schools_ytd <- ggplot(schools_oakridge_nonzero, aes(x=Date, y=PercentPositiveStudentsYearToDate, group=School)) + geom_point(aes(colour=School)) + theme_light() + ylab("Percentage of students testing positive for covid\n(since start of 2021-2 school year)") + xlab("Date") + ggtitle("Student covid infections in Oak Ridge, TN") + scale_color_discrete(guide = FALSE) + scale_y_continuous(sec.axis = sec_axis(~ ., labels=data_ends$Label, breaks = data_ends$PercentPositiveStudentsYearToDate)))
schools_oakridge_nonzero$PercentPositiveStudentsYearToDate <- as.numeric(schools_oakridge_nonzero$PercentPositiveStudentsYearToDate)

schools_oakridge_nonzero$PercentActiveCovidStudents <- as.numeric(schools_oakridge_nonzero$PercentActiveCovidStudents)

try(oakridge_schools_ytd <- ggplot(schools_oakridge_nonzero, aes(x=Date, y=PercentPositiveStudentsYearToDate, group=School)) + geom_point(aes(colour=PercentPositiveStudentsYearToDate)) + scale_colour_gradient2(mid="purple", midpoint=3, high="red", low="blue") + theme_light() + ylab("Percentage of students testing positive for covid\n(since start of 2021-2 school year)") + xlab("Date") + ggtitle("Student covid infections in Oak Ridge, TN") + facet_wrap(~ School, ncol=3) + theme(legend.position = "none"))
print(oakridge_schools_ytd)
```

