---
title: Wastewater Surveillance
output:
  html_document:
    includes:
       in_header: GA_Script.html
---

The [CDC aggregates samples from wastewater](https://covid.cdc.gov/covid-data-tracker/#wastewater-surveillance), as does [Biobot analytics](https://biobot.io/). 

Perhaps the most informative data are from [Biobot analytics](https://biobot.io/), as they show concentration over time (CDC shows change over time or presence/absence only).

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Line plot of covid in wastewater over time", fig.height=20}
source("_packages.R")
tar_load(biobot_sewage)
biobot_sewage_nearby <- subset(biobot_sewage, state %in% c("TN", "NC", "GA"))

try(sewage_biobot <- ggplot(biobot_sewage_nearby, aes(x=date, y=effective_concentration_rolling_average, group=name)) + geom_line(aes(colour=name))+ theme_light() + ylab("Rolling average of covid concentration") + xlab("Date") + ggtitle("Concentration of covid in wastewater") + facet_wrap(~ name, ncol=2) + theme(legend.position = "none"))

print(sewage_biobot)
```

Or zooming in on the last three months:

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Line plot of covid in wastewater over last three months", fig.height=20}
biobot_sewage_90 <- subset(biobot_sewage, Sys.Date() - biobot_sewage$date <= 90)

biobot_sewage_nearby_90 <- subset(biobot_sewage_90, state %in% c("TN", "NC", "GA"))

try(sewage_biobot_90 <- ggplot(biobot_sewage_nearby_90, aes(x=date, y=effective_concentration_rolling_average, group=name)) + geom_line(aes(colour=name))+ theme_light() + ylab("Rolling average of covid concentration") + xlab("Date") + ggtitle("Concentration of covid in wastewater") + facet_wrap(~ name, ncol=2) + theme(legend.position = "none"))

print(sewage_biobot_90)
```

The plots below are all for sliding windows showing change over 15 days. I find them pretty useless, but it's the best the CDC is sharing. I am plotting them by the final date in the window. Some states have great, detailed coverage in the CDC's data -- Tennessee is not one of them. I'm plotting data from the four closest sites to our region. This is based on "closest" of March 27, 2022; it's possible that new sites will come online (for example, UT Knoxville had been [tracking covid in its wastewater](https://cee.utk.edu/wastewater-monitoring-plan-could-keep-campus-safe-from-covid-19/), but these data are not available currently).

The plot below shows the percentage change of covid in wastewater over 15 day intervals: positive means it's increasing over the 15 day period, negative shows it's going down. This is just relative to the window: going up slightly if they're already high or if they're very low means different things for amount of virus in a community. At most, it can decline by 100%; it can increase by a nearly infinite amount. To handle this, I'm plotting it with bounds of -100 to 100% gain over the 15 day interval.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Scatter plot of covid change over time"}
tar_load(sewage)
sewage$ptc_15d[which(sewage$ptc_15d>100)] <- 100
sewage$ptc_15d[which(sewage$ptc_15d<(-100))] <- -100
try(sewage_change <- ggplot(sewage, aes(x=date_end, y=ptc_15d, group=Location)) + geom_point(aes(colour=Location))+ theme_light() + ylab("Percentage change in covid over 15 days") + xlab("Date") + ggtitle("Percentage change in covid over 15 day, bounded by +/- 100%") + ylim(c(-100, 100)) + geom_hline(yintercept = 0) + facet_wrap(~ Location, ncol=2) + theme(legend.position = "none"))

print(sewage_change)
```

This plot shows percentage of samples where covid was detected over a 15 day window.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Scatter plot of covid detection over time"}
try(sewage_detection <- ggplot(sewage, aes(x=date_end, y=detect_prop_15d, group=Location)) + geom_point(aes(colour=Location))+ theme_light() + ylab("Detection of over 15 days") + xlab("Date") + ggtitle("Percentage detection of covid over 15 day interval") + facet_wrap(~ Location, ncol=2) + theme(legend.position = "none"))

print(sewage_detection)
```
