---
title: Travel
output:
  html_document:
    includes:
       in_header: GA_Script.html
---


```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("_packages.R")
source("R/functions.R")
tar_load(tsa_throughput)
tar_load(tysflights)
tsa_throughput$Throughput <- as.numeric(tsa_throughput$Throughput)
tsa_throughput <- tsa_throughput[!is.na(tsa_throughput$Throughput),]

```

Here are TSA screenings nationwide over time, pulled from https://www.tsa.gov/coronavirus/passenger-throughput. Gray for daily data, red for seven day average.

```{r tsa_screenings, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
plot_tsa <- ggplot(tsa_throughput, aes(x=Date, y=Throughput)) + geom_line(colour="gray")+ theme_light() + geom_ma(colour="red", n=7) + guides(linetype = FALSE) +  xlab("Date") + ylab("Number of Screened Passengers")
print(plot_tsa)
```

Plotting on a spiral plot to compare similar high travel times:

```{r tsa_spiral, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
spiral_initialize_by_time(xlim=c(min(tsa_throughput$Date), 365+max(tsa_throughput$Date)),
                          unit_on_axis = "days", period="years",
                          start=90,
                          flip="horizontal")
ymax <- max(tsa_throughput$Throughput)
spiral_track(ylim=c(0, ymax*.9),
             background=FALSE, background_gp = gpar(col = NA, fill = NA))
spiral_polygon(x=c(tsa_throughput$Date, rev(tsa_throughput$Date)),
               y=c(tsa_throughput$Throughput/2, -rev(tsa_throughput$Throughput/2)),
               gp = gpar(col="#d32e2b", fill="#d32e2b50"))
spiral_lines(x=tsa_throughput$Date, y=0)
spiral_text(x="2019-01-01", y=50000, text="2019",
            facing = "curved_inside", just = "right",
            gp=gpar(cex=1, fontfamily="Courier"))
spiral_text(x="2020-01-01", y=50000, text="2020",
            facing = "curved_inside", just = "right",
            gp=gpar(cex=1, fontfamily="Courier"))
spiral_text(x="2021-01-01", y=50000, text="2021",
            facing = "curved_inside", just = "right",
            gp=gpar(cex=1, fontfamily="Courier"))
spiral_text(x="2022-01-01", y=50000, text="2022",
            facing = "curved_inside", just = "right",
            gp=gpar(cex=1, fontfamily="Courier"))
spiral_text(x="2023-01-15", y=50000, text="Jan",
            facing = "curved_inside", just = "centre",
            gp=gpar(cex=1, fontfamily="Courier"))
spiral_text(x="2023-02-15", y=50000, text="Feb",
            facing = "curved_inside", just = "centre",
            gp=gpar(cex=1, fontfamily="Courier"))
spiral_text(x="2023-03-15", y=50000, text="Mar",
            facing = "curved_inside", just = "centre",
            gp=gpar(cex=1, fontfamily="Courier"))
spiral_text(x="2023-04-15", y=50000, text="Apr",
            facing = "curved_inside", just = "centre",
            gp=gpar(cex=1, fontfamily="Courier"))
spiral_text(x="2023-05-15", y=50000, text="May",
            facing = "curved_inside", just = "centre",
            gp=gpar(cex=1, fontfamily="Courier"))			
spiral_text(x="2023-06-15", y=50000, text="Jun",
            facing = "curved_inside", just = "centre",
            gp=gpar(cex=1, fontfamily="Courier"))
spiral_text(x="2023-07-15", y=50000, text="Jul",
            facing = "curved_inside", just = "centre",
            gp=gpar(cex=1, fontfamily="Courier"))
spiral_text(x="2023-08-15", y=50000, text="Aug",
            facing = "curved_inside", just = "centre",
            gp=gpar(cex=1, fontfamily="Courier"))
spiral_text(x="2023-09-15", y=50000, text="Sep",
            facing = "curved_inside", just = "centre",
            gp=gpar(cex=1, fontfamily="Courier"))	
spiral_text(x="2023-10-15", y=50000, text="Oct",
            facing = "curved_inside", just = "centre",
            gp=gpar(cex=1, fontfamily="Courier"))			
spiral_text(x="2023-11-15", y=50000, text="Nov",
            facing = "curved_inside", just = "centre",
            gp=gpar(cex=1, fontfamily="Courier"))			
spiral_text(x="2023-12-15", y=50000, text="Dec",
            facing = "curved_inside", just = "centre",
            gp=gpar(cex=1, fontfamily="Courier"))
								
```



Travel volume differs by day of week. Here, we're comparing 2019 vs 2021 (as travel picks back up). 

```{r tsa_day_of_week, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
tsa_throughput$Day <- weekdays(tsa_throughput$Date)
tsa_throughput$Year <- format(tsa_throughput$Date, "%Y")

tsa_throughput$Day <- factor(tsa_throughput$Day, c( "Monday", "Tuesday", "Wednesday", "Thursday","Friday", "Saturday", "Sunday"))
plot_tsa_day <- ggplot(subset(tsa_throughput, Year!="2020"), aes(x=Day , y=Throughput, fill=Year)) + geom_boxplot()+ theme_light() + xlab("Day") + ylab("Number of Screened Passengers")
print(plot_tsa_day)
```

We can also pull data on [on time performance](https://www.transtats.bts.gov/DL_SelectFields.asp?gnoyr_VQ=FGJ&QO_fu146_anzr=b0-gvzr) from the Bureau of Transportation Statistics to find flights to and from Tyson McGee Airport only. This includes up to Aug. 2021 but gives number of flights and destinations. We can see the number of flights and how the frequency of locations changed over time.

```{r flights_over_time, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
flight_numbers <- tysflights %>% group_by(YEAR) %>% count(DEST_CITY_NAME, ORIGIN_CITY_NAME)
flight_numbers <- flight_numbers[order(flight_numbers$DEST_CITY_NAME, flight_numbers$YEAR),]

departures <- subset(flight_numbers, ORIGIN_CITY_NAME=="Knoxville, TN")
arrivals <- subset(flight_numbers, DEST_CITY_NAME=="Knoxville, TN")
arrivals <- arrivals[order(arrivals$ORIGIN_CITY_NAME, arrivals$YEAR),]

departures_formatted <- data.frame(Year=departures$YEAR, Destination=departures$DEST_CITY_NAME, Number_of_Flights=departures$n)
departures_formatted$Percent_of_Flights <- NA

departures_formatted$Percent_of_Flights[departures_formatted$Year==2019] <- 100*departures_formatted$Number_of_Flights[departures_formatted$Year==2019]/sum(departures_formatted$Number_of_Flights[departures_formatted$Year==2019])

departures_formatted$Percent_of_Flights[departures_formatted$Year==2020] <- 100*departures_formatted$Number_of_Flights[departures_formatted$Year==2020]/sum(departures_formatted$Number_of_Flights[departures_formatted$Year==2020])


departures_formatted$Percent_of_Flights[departures_formatted$Year==2021] <- 100*departures_formatted$Number_of_Flights[departures_formatted$Year==2021]/sum(departures_formatted$Number_of_Flights[departures_formatted$Year==2021])

departures_formatted$Percent_of_Flights <- round(departures_formatted$Percent_of_Flights, 1)


arrivals_formatted <- data.frame(Year=arrivals$YEAR, Origin=arrivals$ORIGIN_CITY_NAME, Number_of_Flights=arrivals$n)
arrivals_formatted$Percent_of_Flights <- NA

arrivals_formatted$Percent_of_Flights[arrivals_formatted$Year==2019] <- 100*arrivals_formatted$Number_of_Flights[arrivals_formatted$Year==2019]/sum(arrivals_formatted$Number_of_Flights[arrivals_formatted$Year==2019])

arrivals_formatted$Percent_of_Flights[arrivals_formatted$Year==2020] <- 100*arrivals_formatted$Number_of_Flights[arrivals_formatted$Year==2020]/sum(arrivals_formatted$Number_of_Flights[arrivals_formatted$Year==2020])


arrivals_formatted$Percent_of_Flights[arrivals_formatted$Year==2021] <- 100*arrivals_formatted$Number_of_Flights[arrivals_formatted$Year==2021]/sum(arrivals_formatted$Number_of_Flights[arrivals_formatted$Year==2021])

arrivals_formatted$Percent_of_Flights <- round(arrivals_formatted$Percent_of_Flights, 1)

arrivals_to_merge <- arrivals_formatted
colnames(arrivals_to_merge) <- gsub("Origin", "City", colnames(arrivals_to_merge))
colnames(arrivals_to_merge) <- gsub("Number_of_Flights", "Arrivals (Number)", colnames(arrivals_to_merge))
colnames(arrivals_to_merge) <- gsub("Percent_of_Flights", "Arrivals (Percent)", colnames(arrivals_to_merge))

departures_to_merge <- departures_formatted
colnames(departures_to_merge) <- gsub("Destination", "City", colnames(departures_to_merge))
colnames(departures_to_merge) <- gsub("Number_of_Flights", "Departures (Number)", colnames(departures_to_merge))
colnames(departures_to_merge) <- gsub("Percent_of_Flights", "Departures (Percent)", colnames(departures_to_merge))

merged_flights <- merge(arrivals_to_merge, departures_to_merge)
merged_flights <- merged_flights[order(merged_flights$City, merged_flights$Year),]

```

### Flights

```{r both, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
row.names(merged_flights) <- NULL
kable(merged_flights)
```
