---
title: UTK 2020-2021 academic year
output:
  html_document:
    includes:
       in_header: GA_Script.html
---


In the 2020-2021 school year, UT published results of saliva tests. ALL students residing in dorms, fraternities, or sororities agreed to testing. This table shows testing results of saliva tests:

```{r utactive, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
source("_packages.R")
tar_load(utk.cases)
utk_plot <- ggplot(utk.cases[!is.na(utk.cases$count),], aes(x=date, y=count, group=group)) + geom_line(aes(colour=group)) + ylab("Number of active cases at UTK") + xlab("Date") + ylim(0,NA) + scale_colour_viridis_d(end=0.8)
print(utk_plot)
```

We can also use the UTK saliva data to estimate the number of new cases in the 2020-2021 school year: the proportion of students who ultimately test postive out of those tested by the saliva scans. Given poor compliance, the true proportions may be much higher than this (if students want to endanger others by not isolating, they may avoid testing if they think they have been exposed).  

I am converting the saliva test info to new cases per 100K. I am adopting the assumption that Knox County uses that new cases are only active for 14 days, so I'm computing the new case estimate as 1/14 the active case estimate.  I include the 95% confidence interval for the estimate of new cases per 100,000 people, though this is an underestimate of the uncertainty (are dorms good random samples or are results clustered, are students who refuse testing similar to those who get tested, etc.).

**Note this is for the 2020-2021 school year**: to my knowledge, there is no such data gathering planned for 2021-2022.


```{r plotsaliva100k, echo=FALSE, message=FALSE, warning=FALSE}
tar_load(saliva_data)
saliva_plot <- ggplot(saliva_data, aes(x=DATE, y=New_cases_per_100k)) + 
#geom_rect(mapping=aes(xmin=min(DATE), xmax=Sys.Date(), ymin=0, ymax=1), fill="darkolivegreen1") +
#  geom_rect(mapping=aes(xmin=min(DATE), xmax=Sys.Date(), ymin=1, ymax=10), fill="khaki1") +
#  geom_rect(mapping=aes(xmin=min(DATE), xmax=Sys.Date(), ymin=10, ymax=25), fill="tan1") +
#  geom_rect(mapping=aes(xmin=min(DATE), xmax=Sys.Date(), ymin=25, ymax=max(New_cases_per_100k_upper)), fill="indianred1") + 
geom_point() + ylab("Est. daily new cases 100,000 people based on UTK saliva samples") + xlab("Date") + ylim(0,NA) + scale_colour_viridis_d(end=0.8) + geom_errorbar(aes(ymin=New_cases_per_100k_lower, ymax=New_cases_per_100k_upper), width=0.1) + ggtitle("Saliva results 2020-2021 school year")
print(saliva_plot)
```

We can also see the compliance rate of students with testing. For 2020-2021, all students signed a pledge showing their willingness to abide by community standards. Those in residence at UT agreed to saliva testing. 

**Note this is for the 2020-2021 school year**: to my knowledge, there is no such data gathering planned for 2021-2022.

```{r plotsalivacompliance, echo=FALSE, message=FALSE, warning=FALSE}
saliva_data$Participation.percentage <- 100*saliva_data$Participation.rate
saliva_compliance <- ggplot(saliva_data, aes(x=DATE, y=Participation.percentage)) + 
geom_line() + ylab("Percentage of resident students participating in mandatory teseting") + xlab("Date") + ylim(0,100) + ggtitle("Saliva compliance 2020-2021 school year")
print(saliva_compliance)
```


