---
title: UTK 2021-2022 academic year
output:
  html_document:
    includes:
       in_header: GA_Script.html
---


Official information about covid at UTK available at https://www.utk.edu/coronavirus/guides/data-monitoring-and-contingency-options. CDC guidance for institutions of higher education who don't require vaccination, which includes UTK, is [here](https://www.cdc.gov/coronavirus/2019-ncov/community/colleges-universities/considerations.html#section3). Some of the other dashboards other the the one below:

* [UTK's Covid Dashboard](https://www.utk.edu/coronavirus/guides/data-monitoring-and-contingency-options.html). Updated weekdays
* [UT System Dashboard](https://tennessee.edu/coronavirus/dashboard/). Updated daily, with a potential for filtering by campus
* [Alex Zukowski Dashboard](https://sites.google.com/view/utk-covid19). Created by a UTK student.

UTK released [some data](https://www.utk.edu/coronavirus/guides/data-monitoring-and-contingency-options/), though less than some peers or UTK itself last academic year. They stopped releasing data after May 20, 2022.

The first plot shows the percentage of students and employees with active covid cases *known to UTK* at any one time. I am curious about the overall trend in each, as well as about which group has more reported cases at the moment. One guess could be that covid proportion might be higher among students (high density housing, generally lower vaccination rate for younger populations), but they might get tested at lower rates. Approximate total population size in each group comes from the Chancellor's update of Aug. 19, 2021.

Note that UTK's data is released [here](https://www.utk.edu/coronavirus/guides/data-monitoring-and-contingency-options/).

```{r utk2021, echo=FALSE, message=FALSE, warning=FALSE}
source("_packages.R")
tar_load(utk_active_cases_reported)
tar_load(zukowski_data)
tar_load(knox17to25)
utk_active_cases_pivoted <- data.frame(DATE=rep(utk_active_cases_reported$DATE,2), PercentageActive=100*c(utk_active_cases_reported$ProportionFacultyStaff, utk_active_cases_reported$ProportionStudents), Population=c(rep("Employees", nrow(utk_active_cases_reported)),rep("Students", nrow(utk_active_cases_reported) )))
#utk_active_cases_pivoted <- data.frame(DATE=rep(zukowski_data$DATE,2), PercentageActive=as.numeric(gsub('%', '', c(zukowski_data$CASES_ACTIVE_EMPLOYEES_PERPOP, zukowski_data$CASES_ACTIVE_STUDENTS_PERPOP))), Population=c(rep("Employees", nrow(zukowski_data)),rep("Students", nrow(zukowski_data) )))

utk_active_cases_pivoted_plot <- ggplot(subset(utk_active_cases_pivoted, DATE>="2021-08-01"), aes(x=DATE, y=PercentageActive, group=Population, colour=Population)) +  geom_line() + ylab("Percent with active covid infections reported to UTK") + xlab("Date") + ylim(0,0.1+round(max(utk_active_cases_pivoted$PercentageActive)))  + scale_colour_viridis_d(end=0.8) + theme_light() 

print(utk_active_cases_pivoted_plot)
```

There is also data on those who are receiving active covid support from UTK.

```{r utk2021isolations, echo=FALSE, message=FALSE, warning=FALSE}

tar_load(utk_isolations_reported)
utk_isolations_plot <- ggplot(subset(utk_isolations_reported, DATE>="2021-08-01"), aes(x=DATE, y=Percentage, group=Population, colour=Population)) +  geom_line() + ylab("Percent receiving support for covid at UTK") + xlab("Date") + ylim(0,NA)  + scale_colour_viridis_d(end=0.8) + theme_light() 
#utk_isolations_pivoted <- data.frame(DATE=rep(zukowski_data$DATE,3), Percentage=as.numeric(gsub('%', '', c(zukowski_data$SELF_ISOLATED_NRS_TOTAL_PERPOP, zukowski_data$SELF_ISOLATED_RS_TOTAL_PERPOP, zukowski_data$SELF_ISOLATED_E_TOTAL_PERPOP))), Population=c(rep("Students (residential)", nrow(zukowski_data)),rep("Students (non-residential)", nrow(zukowski_data)), rep("Employees", nrow(zukowski_data))))

#utk_isolations_plot <- ggplot(subset(utk_isolations_pivoted, DATE>="2021-08-01"), aes(x=DATE, y=Percentage, group=Population, colour=Population)) +  geom_line() + ylab("Percent reporting self-isolation to UTK\n(quarantine or isolation)") + xlab("Date") + ylim(0,.1+round(max(utk_isolations_pivoted$Percentage)))  + scale_colour_viridis_d(end=0.8) + theme_light() 

print(utk_isolations_plot)
```

Unlike [over 1,125 other colleges and universities](https://www.chronicle.com/blogs/live-coronavirus-updates/heres-a-list-of-colleges-that-will-require-students-to-be-vaccinated-against-covid-19), UTK has no vaccination mandate nor mask mandate in general (there may be exceptions in particular areas, like nursing with high patient contact). 
