---
title: Year Comparison
output: html_document
params:
  daily_focal: "unknown"
  schoolkids_daily: "unknown"
---

<h2 id="dejavu">Comparing last academic year with this academic year</h2>

In the over 20 months since covid started spreading we have learned a lot: vaccines are now available (in the US), we know masks help, and so forth. However, the virus continues to evolve, too. 

We can see how students age 5-18 (so equivalent to K-12, generally) have had positive cases in East Tennessee.

```{r dejavuschoolkids, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Line plot of cases in children 5-18 in 2020 vs 2021"}
source("_packages.R")
tar_load(daily_focal)
tar_load(schoolkids_daily)


schoolkids_daily_by_year <- schoolkids_daily
schoolkids_daily_by_year$Year <- format(schoolkids_daily_by_year$DATE, format="%Y")
schoolkids_daily_by_year$MONTH_DAY_IFFY_YEAR <- as.Date(as.POSIXct(paste0("2021-",format(schoolkids_daily_by_year$DATE, format="%m-%d"), "%Y-%m-%d"))) #the year isn't right for some, but this helps plotting
schoolkids_daily_by_year <- subset(schoolkids_daily_by_year, Region=="East TN")
try(student_covid_daily_by_year_plot <- ggplot(schoolkids_daily_by_year, aes(x=MONTH_DAY_IFFY_YEAR, y=NEW_CASES, group=Year)) + theme_light() + geom_ma(aes(colour=Year, linetype="a")) +  guides(linetype = "none") + ylab("New cases for age 5-18 students, 7 day avg") + xlab("Date") + ggtitle("New Age 5-18 student cases in East Tennessee by year") + scale_x_date(date_labels = "%b", breaks = "2 months", limits=c(as.Date("2021-01-01", format="%Y-%m-%d"), as.Date("2021-12-31", format="%Y-%m-%d"))) + scale_color_manual(values=c("darkgray",'red')) + theme(legend.position='top', legend.justification='left',legend.direction='horizontal'))
try(print(student_covid_daily_by_year_plot))
```

Or positive covid cases across all individuals:

```{r dejavucases, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Line plot of cases in 2020 vs 2021"}
daily_focal_by_year <- daily_focal[!is.na(daily_focal$NEW_HOSPITALIZED),]
daily_focal_by_year <- subset(daily_focal_by_year, Region=="East TN")

daily_focal_by_year$Year <- format(daily_focal_by_year$DATE, format="%Y")
daily_focal_by_year$MONTH_DAY_IFFY_YEAR <- as.Date(as.POSIXct(paste0("2021-",format(daily_focal_by_year$DATE, format="%m-%d"), "%Y-%m-%d"))) #the year isn't right for some, but this helps plotting

try(daily_case_by_year_plot <- ggplot(daily_focal_by_year, aes(x=MONTH_DAY_IFFY_YEAR, y=NEW_CASES, group=Year)) + theme_light() + geom_ma(aes(colour=Year, linetype="a")) +  guides(linetype = "none") + ylab("New cases per day\n(7 day average)") + xlab("Date") + ggtitle("Cases in different years in East TN") + scale_x_date(date_labels = "%b", breaks = "2 months", limits=c(as.Date("2021-01-01", format="%Y-%m-%d"), as.Date("2021-12-31", format="%Y-%m-%d"))) + scale_color_manual(values=c("darkgray",'red')) + theme(legend.position='top', legend.justification='left',legend.direction='horizontal'))
try(print(daily_case_by_year_plot))
```


Or deaths over time across all individuals:

```{r dejavudeath, echo=FALSE, message=FALSE, warning=FALSE, fig.alt="Line plot of deaths in 2020 vs 2021"}
try(daily_death_by_year_plot <- ggplot(daily_focal_by_year, aes(x=MONTH_DAY_IFFY_YEAR, y=NEW_DEATHS, group=Year)) + theme_light() + geom_ma(aes(colour=Year, linetype="a")) +  guides(linetype = "none") + ylab("Deaths per day\n(7 day average)") + xlab("Date") + ggtitle("Deaths in different years in East TN") + scale_x_date(date_labels = "%b", breaks = "2 months", limits=c(as.Date("2021-01-01", format="%Y-%m-%d"), as.Date("2021-12-31", format="%Y-%m-%d"))) + scale_color_manual(values=c("darkgray",'red')) + theme(legend.position='top', legend.justification='left',legend.direction='horizontal')) 
try(print(daily_death_by_year_plot))
```
